\begin{itemize}
\item {\bf University of Delhi}, North Delhi, Delhi, India. \hfill{Jan 2018 -- Jun 2018}\\
{\ Masters Dissertation}\\
Mentor - {\em Prof. Patrick Das Gupta}\\
Project - {\em Statistical Studies of Pulsar Transverse Velocities and the Nulling Phenomena}

\item {\bf NCRA-TIFR\footnote{National Centre for Radio Astrophysics - Tata Institute of Fundamental Research}}, Pune, Maharashtra. India. \hfill{May 2017 -- July 2017}\\
{\em Summer Research Fellow}, \href{https://drive.google.com/file/d/1DNbjEN0h9-dH9aIKz8tkRyhW-5-YZbuX/view?usp=sharing}{Indian Academies of Sciences}\\
Mentor - {\em Dr. Sushan Konar}\\
Project - {\em Statistical Studies of Nulling Radio Pulsars}

\item {\bf University of Delhi}, North Delhi, Delhi. India. \hfill{Aug 2015 -- Oct 2016}\\
{\em Student Researcher}, \href{https://drive.google.com/file/d/1s8Hox6czF8egijzbA-QVuBYGypyfTwqZ/view?usp=sharing}{Innovation Project 2015-16}\\
Mentor - {\em Dr. N. Rathnasree}, Director, Nehru Planetarium, New Delhi\\
Project Supervisor - {\em Dr. Ashok Kumar}, Associate Professor, Ramjas College, Univ. of Delhi\\
Project - {\em An Interdisciplinary Study of Light Pollution in Indian Context}

\item {\bf SINP\footnote{Saha Institute of Nuclear Physics}}, Kolkata, West Bengal. India. \hfill{May 2015 -- Jun 2015}\\
{\em Summer Associate}, \href{https://drive.google.com/file/d/1wfS8LcFg6AJY0KyVaGBmRqpGs7vaNn4s/view?usp=sharing}{Undergraduate Associateship programme}\\
Mentor - {\em Prof. Pradip K. Roy}, HENPP\footnote{High Energy Nuclear and Particle Physics} Division\\
Reading project on  {\em Quantum Field Theory (Phenomenology)}

\item {\bf SINP}, Kolkata, West Bengal. India. \hfill{May 2014 -- Jul 2014}\\
{\em Summer Associate}, \href{https://drive.google.com/file/d/1wfS8LcFg6AJY0KyVaGBmRqpGs7vaNn4s/view?usp=sharing}{Undergraduate Associateship programme}\\
Mentor - {\em Prof. Parthasarathi Mitra}, Theory division\\
Reading project on  {\em Quantum Field Theory (Phenomenology)}
\end{itemize}