\begin{itemize}[noitemsep]
{
\item \href{https://www.icts.res.in/program/gws2023}{Summer School on GW Astronomy}. ICTS, Bengaluru. \hfill{Jul-Aug 2023}
\item (School) \href{https://icts.res.in/program/BigDataCosmo}{Largest Cosmological Surveys and Big Data Science}. ICTS, Bengaluru.\hfill{May 2023}
\item (Discussion Meeting) \href{https://www.icts.res.in/discussion-meeting/LGWD}{Lunar Gravitational-Wave detection}. ICTS, Bengaluru. \hfill{Apr 2023}
\item \href{https://www.icts.res.in/program/gws2022}{Summer School on GW Astronomy}. ICTS, Bengaluru. \hfill{May-Jun 2022}
\item (School) \href{https://www.icts.res.in/program/peu2022}{Physics of the Early Universe}. ICTS, Bengaluru. \hfill{Jan 2022} 
\item \href{https://www.icts.res.in/program/gws2021}{Summer School on GW Astronomy}. ICTS, Bengaluru. \hfill{Jul 2021}
\item (Workshop) \href{https://events.iitgn.ac.in/2020/TGRGW/}{Testing General Relativity using Gravitational Waves}. IIT, Gandhinagar. \hfill{Aug 2020}
\item \href{https://www.gw-openscience.org/static/workshop3/}{GW Open Data workshop 3}. LIGO-VIRGO collaboration. \hfill{May 2020}
\item \href{https://www.icts.res.in/program/gws2020}{Summer School on GW Astronomy}. ICTS, Bengaluru. \hfill{May 2020}
\item (Discussion Meeting) \href{https://www.icts.res.in/discussion-meeting/smbh2019}{Astrophysics of Supermassive Black Holes}. ICTS, Bengaluru. \hfill{Dec 2019}
\item \href{https://www-apps.iucaa.in/Stu-Prog-ISSIA.html}{IUCAA Summer School for Astronomy and Astrophysics}. IUCAA, Pune. \hfill{May -- Jun 2016}
\item (Seminar) Hundred Years of Einstein's Theory of Relativity, University of Delhi, Delhi. \hfill{2015}
}\end{itemize}